---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Translations from the Collaboration Campfire

This repo provides translation files for the 
"How to Contribute to a Translation Team" [Collaboration Campfire](https://contributor.r-project.org/events/collaboration-campfires).

The `po_dir_setup.R` script provides code to 

1. Extract the `po` directories from 
a local copy of the R sources (e.g. a git checkout of r-devel/r-svn) and put 
them in this repo in a directory named by the current version of R-devel.
2. Download the source code for the recommended packages, extract the 
corresponding `po` directories (if they exist for the package) and put them in 
the `Recommended` directory of this repo.

The `branch_setup.R` script provides code to set up branches for each language, 
removing files for other languages for convenience.

The `create-todo.R` script provides code to create an issue with a TODO list 
for each language. The TODO is a checklist of all `.pot` files, checked off 
if there exists a corresponding `.po` file for that language, with all 
messages translated and none marked as fuzzy.

The `check_progress.R` script provides code to check progress for a given 
language, producing a table as follows

```{r}
lang <- "de"
library(devtools)
po_status <- source_url("https://raw.githubusercontent.com/r-devel/translations-campfire/main/check_progress.R")
knitr::kable(po_status$value)
```

